Robust Estimation, Prediction and Control with \\ Linear Dynamics and Generic Costs

### 2020-02-03 main.tex
Update intro

Since experiencing failures is out of question, the only way to prevent them from the outset, when the system is first deployed, is to rely on some sort of prior knowledge. In this work, we assume that the system dynamics are partially known, in the form of a parametrized dynamical system with unknown parameters. We argue that this assumption is realistic given that most industrial applications to date have been relying on physical models to describe their processes and engineered controllers to operate them, rather than machine learning. Our framework relaxes this modelling effort by allowing some structured uncertainty around the nominal model. We adopt a data-driven scheme where we wish to estimate the parameters more accurately as we interact with our true system. Most model-based reinforcement learning algorithms only rely on the estimated dynamics to derive the corresponding optimal controller, but these methods often suffer from \emph{model bias}: they ignore the error that exists between the learned and true dynamics, which can dramatically degrade the control performances \citep{Schneider1997}.

To address this issue, we turn to the framework of \emph{robust} decision-making: instead of merely considering a point estimate of the dynamics, we build an entire \emph{confidence region} that contains the true dynamics with high probability, and optimise the decisions so as to maximise the worst-case outcome with respect to this uncertainty. Minimax problem are hard to solve, especially since $R$ can be arbitrary. We cannot use traditional tools from the robust LQ control community (coarse-id control, system-level synthesis). Instead, we adopt a hierachical control architecture, controller selection: discrete choice of a driving maneuver, a short-term goal, whose execution is performed by a fixed low-level controller. It is true that the passage from continuous optimization to discrete optimization induces a suboptimality. However, it can be mitigated by using a more diverse controller basis. We are left with a sequential optimization problem with continuous states and discrete actions: tree-based planning algorithms. But not a point estimate, a whole confidence region. Hence, a two step procedure: robust prediction of the reachability set, which provides a conservative pessimistic reward to the planning algorithm.

>>>>

Since experiencing failures is out of question, the only way to prevent them from the outset, when the system is first deployed, is to rely on some sort of prior knowledge. In this work, we assume that the system dynamics are partially known, in the form of a parametrized dynamical system with unknown parameters. We argue that this assumption is realistic given that most industrial applications to date have been relying on physical models to describe their processes and engineered controllers to operate them, rather than machine learning. Our framework relaxes this modelling effort by allowing some structured uncertainty around the nominal model. We adopt a data-driven scheme where we wish to estimate the parameters more accurately as we interact with the true system. Most model-based reinforcement learning algorithms only rely on the estimated dynamics to derive the corresponding optimal controller, but these methods often suffer from \emph{model bias}: they ignore the error that exists between the learned and true dynamics, which can dramatically degrade the control performances \citep{Schneider1997}. In particular, the framework of maximising an objective under constraints naturally pushes systems to operate in the vicinity of constraint saturation, which makes it more prone to failure when the model is imperfect.

To address this issue, we turn to the framework of \emph{robust} decision-making: instead of merely considering a point estimate of the dynamics, we build an entire \emph{confidence region} that contains the true dynamics with high probability, and optimise the decisions so as to maximise the worst-case outcome with respect to this uncertainty. Minimax problem are hard to solve, especially since the reward function $R$ can be arbitrary. In particular, this keeps us from employing traditional tools from the robust synthesis literature, such as $\cH_\infty$ \todo{(ref needed)} control or system-level synthesis \todo{(ref needed)}. Since we are optimising a generic reward function, we turn to more general sequential optimisation algorithms. The continuous state space prevents us from using dynamic programming techniques, so we consider tree-based planning instead. Though some work address continuous actions \todo{ref needed}, we resort to a first approximation and discretise the decision space by adopting a hierarchical control architecture. We  formulate the problem high-level decision of selecting a low-level controller among a finite basis \todo{(ref from temporal abstraction)}. For instance, this could amount to choosing a short-term goal to follow, or a skill to execute such as a driving maneuver. The passage from continuous to discrete optimization induces a suboptimality, but it can be mitigated by diversifying the controller basis. These low-level controllers are not learnt, which also constitutes a limitation \todo{realistic in industrial setting?}. However, tree-based planning algorithms are designed to optimise a singled known generative model, and not a whole confidence region. Hence, we adapt them to the robust framework by following a two step procedure: we first predict of the set of states that can be reached by following a control sequence, under all possible dynamics. This reachability set is used to provide a conservative pessimistic reward to the planning algorithm.
